A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing

### 2019-08-30 paper/main.tex
udpated k-optimization term

We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
\[
  \argmax_K \left[POM(\frac{a}{b+J}) - \frac{K}{\alpha}\right],
\]
where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was an arbitrary constant used to ensure a positive denominator, set equal to 100; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).  Before subtracting the regularization term, we scaled the ratio of correlations to be a proportion of the maximum ratio across all $K$'s.  Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kcorrs~for the values of \textit{a} and \textit{b} for each $K$, Fig.~\kopt~for the optimization functions for the video and recalls).  After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.  This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.

>>>>

We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
\[
  \argmax_K \left[POM(\frac{a}{b-J}) - \frac{K}{\alpha}\right],
\]
where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was a constant used to ensure a positive denominator, set equal to $\min_K\left[{\frac{a}{b}}\right]$; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).  Before subtracting the regularization term, we scaled the ratio of correlations to be a proportion of the maximum ratio across all $K$'s.  Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kcorrs~for the values of \textit{a} and \textit{b} for each $K$, Fig.~\kopt~for the optimization functions for the video and recalls).  After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.  This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
